Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

For cases in the upper triangular of \cref{tab:desth}, $E[H_S] < E[H_D]$,
which means most triplets will be turned into adversarial example by HM
to increase the hardness.
%
Although most of such cases end up with model collapse, the preliminary 
result suggests that HM from random to semihard is effective in significantly
improve the robustness without model collapse, at an expected cost on the R@1
performance on benign examples.

As the samples will not become adversarial once $H_S>H_D$ (zero perturbation in
this case according to \cref{eq:hm}, an effective combination of source and
destination sampling strategy should make the expectation of source hardness
less than the source hardness, \ie, $E[H_S]<E[H_D]$.
%
Namely, the source sampling strategy should be ahead of the destination
sampling strategy in this list.

@@

The proposed hardness manipulation is effective.

>>>>

For cases in upper triangular of \cref{tab:desth}, $E[H_S] \leqslant E[H_D]$,
which means most triplets will be turned into adversarial example by HM
to increase the hardness.
%
Although most of such cases end up with model collapse, the preliminary 
result suggests that HM from random to semihard is effective in significantly
improve the robustness without model collapse, at an expected cost on the R@1
performance on benign examples.

For cases in lower triangular of \cref{tab:desth}, $E[H_S] \geqslant E[H_D]$,
which means most tirplet will not be turned into adversarial according to
\cref{eq:hm}.
%
In such cases, the model will not be able to effectively learn from a strong
adversary, and hence will behave as if no defense is equipped.
%
As an exception, HM from softhard to semihard can also lead to relatively high
adversarial robustness.
%
Due to the high variance of hardness of softhard sampling strategy, the
hardness of a notable portion of triplets will be less than that of semihard,
and hence HM will create some adversarial examples for training.
%
In other words, HM in this case can be interpreted as mixing some unperturbed
softhard triplets and some semihard adversarial triplets.

@@

The proposed hardness manipulation is effective.
\oo{todo: table of first and second order central moment}
